Computer Science House By-Laws

### 2016-04-11 bylaws.tex
Selection of Advisory Members
Proposed amendment for 4.B.4 - Selection of Advisory Members.

	\item Ballots will then be distributed for a secret ballot, fifty-percent House vote, as defined in \ref{Fifty Percent}.
		If more than two advisors are selected via this process, the Executive Board may call for a revote amongst the candidates selected in order to reduce the number of advisors to a workable level.
		If this decision is made, the candidates selected in the first ballot become the nominees for the second ballot and Step Three and Four are repeated.
		This recast process may not be repeated a second time.

@@

		If one or more selected candidates decline the position, the Executive Board may begin a selection process for additional advisors.
		Note that selected candidates who accept their selection remain selected, this additional selection process is only a means to bring the number of advisors up to a workable level.
		If the additional advisor selection process is initiated, repeat Steps One through Five with the original nominations plus any additional nominations.

>>>>

    \item Ballots are distributed for each nominee as a fifty-percent House vote defined in \ref{Fifty     
        Percent}. Voting must remain open for a minimum of a forty-eight hour period. 

@@
